\documentclass[11pt]{article}
    \usepackage[a4paper]{geometry}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{hyperref}
    \usepackage{textcomp}
    \usepackage{enumitem}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \textheight=10in
    \pagestyle{empty}
    \raggedright

    %\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-10pt} \hrulefill \\
}

\newcommand{\header} [1] {
    \begin{center}
      {\large \scshape {#1}}
      \lineunder
    \end{center}
    \vspace*{-8pt}
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\profile} [5] {
    \vspace*{-15pt}
    \begin{center}
        {\huge \scshape \textbf{#1}}\\
        \vspace{1mm}
        \small {#2} $\cdot$ {#3} $\cdot$ {#4} $\cdot$ {#5}
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\vspace*{-40pt}

%==== Profile ====%
\profile{Cil Satriawan}{Bandung, Indonesia}{(62)821-3163-8069}
{cil.satriawan@gmail.com}{\href{https://www.linkedin.com/in/cil-satriawan-a60601111}{LinkedIn}}

%==== Cover Letter ====%
\header{Cover Letter}
\vspace{1mm}

Practical AI is currently past the point of disruption, yet not quite
ubiquitous. As entry costs and the initial adoption hurdle are overcome, I
believe the following decade will mark the entry of AI into all facets of daily
life. Given the current zeitgeist with regards to AI, its world-class AI
expertise and rapid growth, AssemblyAI sounds like an incredibly exciting place
to work at. I would love to contribute my experience to the team in any capacity.
\vspace{3mm}

I am an engineer and manager currently based in Indonesia with prior experience
in the AI space. I am relocating to London in Augutst 2023, where my partner
will be pursuing a postgraduate degree. I grew up in various Commonwealth
countries and consider English my mother tongue.
\vspace{3mm}

In the past 5 years I have founded a software house and joined an
AI start-up, both of which I am currently active in. As founder of a software
house primarily in the banking domain, I am involved in both business and
technical decisions, often assuming PM duties and interacting with clients as
needed. As VP Engineering of an AI start-up, I am responsible for hiring,
onboarding, KPIs, and growing teams. I maintain mostly high-level technical
duties, mainly surrounding design and architecture, but still code and conduct
code reviews regularly.
\vspace{3mm}

As an engineer and manager, I find satisfaction when various disparate elements
click together to achieve a single purpose, be it for software systems or teams
of people. I am usually there to facilitate the building process, ensuring it
can be done reliably, sustainably, and quickly (enough). In teams as in systems,
I have learnt that communication is key: Transparency, clarity, brevity, and a
large degree of tolerance is needed to make teams and teams of teams function
robustly. I believe I can bring this experience with me as an engineering
manager at Scandit, and further advance this skill for the benefit of
the organization.
\vspace{3mm}

Ambiguity and fluidity of roles is unaviodable in a fast moving development
environment, where specs and direction may change rapidly. In a given
development cycle, I have had to assume the role of product owner, project
manager, developer, and operations, oftentimes across multiple projects and
products. Rapidly iterating, occasionally discarding, and eventually refactoring
systems for performance within strict timelines is something I contend with
regularly. I believe this kind of flexibility will be a boon for the team, given
the disruptive nature of the product and the amount of work still to be done to
displace legacy technologies.
\vspace{3mm}

I would be delighted to discuss the ways in which I could contribute to the
AssemblyAI team in greater detail. I look forward to hearing from you.
\vspace{3mm}

Kind regards,\newline
Cil Satriawan

\ 
\end{document}
