\documentclass[11pt]{article}
    \usepackage[a4paper]{geometry}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{hyperref}
    \usepackage{textcomp}
    \usepackage{enumitem}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \textheight=10in
    \pagestyle{empty}
    \raggedright

    %\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-10pt} \hrulefill \\
}

\newcommand{\header} [1] {
    \begin{center}
      {\large \scshape {#1}}
      \lineunder
    \end{center}
    \vspace*{-8pt}
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\profile} [5] {
    \vspace*{-15pt}
    \begin{center}
        {\huge \scshape \textbf{#1}}\\
        \vspace{1mm}
        \small {#2} $\cdot$ {#3} $\cdot$ {#4} $\cdot$ {#5}
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\vspace*{-40pt}

%==== Profile ====%
\profile{Cil Satriawan}{Bandung, Indonesia}{(62)821-3163-8069}
{cil.satriawan@gmail.com}{\href{https://www.linkedin.com/in/cil-satriawan-a60601111}{LinkedIn}}

%==== Cover Letter ====%
\header{Cover Letter}
\vspace{1mm}

I am a software engineer and manager currently based in Bandung, Indonesia with
5 years of prior experience in the AI space building large-scale systems as both
an individual contributor and lead. 
\vspace{3mm}

In the past 5 years I have founded a software house and joined an AI start-up,
both of which I am currently active in. As VP Engineering of an AI start-up,
I am responsible for hiring, onboarding, growing, and assessing teams. I maintain
high-level technical duties, mainly surrounding design and architecture, and code
and review code regularly. As the founder of a software house dealing primarily
in the banking domain, I am involved in both business and technical decisions,
often assuming PM duties and interacting with clients as needed.
\vspace{3mm}

I have a formal background in machine learning, specifically speech processing.
Along with work experience in digital signal processing, this has been helpful
in building AI systems geared towards speech processing and computer vision.
Some examples include a national-scale voice biometrics system and a COVID
surveillance system for local governments aiming to detect large congregations
of people and face mask prevalence from public webcams. 
\vspace{3mm}

I am a native Indonesian speaker, but consider English my first language. I
was born in Canada and spent a total of 12 years in English-speaking countries
during my formative years. I have spent the past 3 years working almost entirely
remotely, and reside primarily in Bandung, with frequent visits to Bogor and
Jakarta. However, over the next 2 years I will occasionally be travelling to
London where my partner is temporarily residing.
\vspace{3mm}

I would be delighted to discuss the ways in which I could contribute to the
Revalue Nature team in greater detail. I look forward to hearing from you.
\vspace{3mm}

Kind regards,\newline
Cil Satriawan

\ 
\end{document}
