\documentclass[a4paper]{article}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{hyperref}
    \usepackage{textcomp}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \textheight=10in
    \pagestyle{empty}
    \raggedright

    %\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

    \begin{document}
\vspace*{-40pt}

    

%==== Profile ====%
\vspace*{-30pt}
\begin{center}
	{\Huge \scshape {Cil Satriawan}}\\
	Bandung, Indonesia $\cdot$ (62) 821-3163-8069 $\cdot$ cil.satriawan@gmail.com 
        $\cdot$ \href{https://www.linkedin.com/in/cil-satriawan-a60601111}{LinkedIn}\\
\end{center}

%==== Work Experience ====%
\header{Work Experience}
\vspace{1mm}

\textbf{Prosa} \hfill Bandung, Indonesia\\
\textit{VP Engineering} \hfill Jan 2022 -\\
\vspace{-3mm}
\begin{itemize} \itemsep -2pt
  \item Grew the engineering division (SWE, DevOps, QA) from 25 to 60 engineers.
  \item Implemented an engineering management structure/track through the
    coaching of tech leads.
  \item Improved year-on-year retention rate by 50\% through the adoption of
    company-wide 1-on-1s.
  \item Improved time-to-productivity through appointment of dedicated
    onboarding mentors and development of onboarding material.
  \item Led the end-to-end development of Conversa, a SaaS and on-premise
    enterprise chatbot system, using domain-driven and agile methodologies.
\end{itemize}
\vspace{-3mm}
\textit{Systems Lead} \hfill Jun 2019 - Dec 2021\\
\vspace{-3mm}
\begin{itemize} \itemsep -2pt
  \item Supervised and managed the DevOps engineers of the Systems team.
  \item Designed and led the development of systems, projects, and products
    organization-wide.
\end{itemize}
\vspace{-3mm}
\textit{Speech AI Engineer} \hfill Jan 2018 - Jan 2020\\
\vspace{-3mm}
\begin{itemize} \itemsep -2pt
  \item Designed and implemented the Voice ID biometric speech system, worth USD
    \$270,000 annually.
  \item Speech-related research; data collection and pre-processing, modeling,
    and experiment design.
\end{itemize}

\vspace{-2mm}
\textbf{Agranara} \hfill Jakarta, Indonesia\\
\textit{Co-Founder and CTO} \hfill Dec 2017 -\\
\vspace{-3mm}
\begin{itemize} \itemsep -2pt
  \item Designed and led the development of several large information systems in
    the banking and geospatial sectors, closing projects worth a combined total of
    USD \$500k.
  \item Lead and manage multiple development teams, totalling 20 engineers.
\end{itemize}

\vspace{-2mm}
\textbf{Institut Teknologi Bandung} \hfill Bandung, Indonesia\\
\textit{Graduate Research Assistant} \hfill Sep 2015 - Sep 2017\\
\vspace{-3mm}
\begin{itemize} \itemsep -2pt
  \item Researched and developed an AI meeting transcription system in
    collaboration with PT INTI.
  \item Academic assistant for undergraduate-level speech machine learning courses.
\end{itemize}

\vspace{-2mm}
\textbf{Kuassa} \hfill Bandung, Indonesia\\
\textit{DSP Engineer} \hfill May 2012 - Sep 2015\\
\vspace{-3mm}
\begin{itemize} \itemsep -2pt
  \item Designed and implemented VST plugins for audio and musical applications.
  \item Utilize various technologies for the simulation of analog audio
    equipment.
\end{itemize}

%==== Education ====%
\header{Education}
\vspace{1mm}

\textbf{Institut Teknologi Bandung}\hfill Bandung, Indonesia\\
\vspace{-3mm}
\begin{itemize} \itemsep -2pt
  \item Master in Informatics Engineering \textit{GPA 3.75} \hfill Sep 2015 - Jun 2018
  \item Bachelor in Informatics Engineering \hfill Sep 2008 - October 2014
\end{itemize}
% \vspace{-2mm}
% \textbf{National Junior College}\hfill Singapore\\
% \hfill Oct 2003 - Dec 2007\\

%==== Skills ====%
\header{Skills \& Interests}
\vspace{2mm}
\hspace{-4mm}
\begin{tabular}{ l l }
\textbf{Coding:} & Python, PHP, C/C++, Javascript/Typescript, Java, Go,
PostgreSQL, Redis, Kafka,\\
\vspace{1mm}
                 & Docker, Kubernetes, Terraform, GCP, Linux\\

\textbf{Tools}:
\vspace{1mm}
& Agile, Scrum, Waterfall, Microservices, DDD, TDD, CI/CD \\

\textbf{Interests:}
\vspace{1mm}
& Audio Engineering, Music Production, Open Source Software, Applied ML\\

\end{tabular}
\vspace{2mm}

%==== Experience ====%
\header{Experience}
\vspace{1mm}

{\textbf{Conversa}} {\sl Python, React, PyTorch, Java, ejabberd} \hfill Jun 2022 -\\
Chatbot system implemented as a collection of domain-driven microservices for
enterprise SaaS and on-premise use. Consists of authorization, chatbot builder,
chatbot engine, deployment, omnichannel, and human agent services.\\
\vspace*{2mm}

{\textbf{Voice ID}} {\sl Python, C++, Java, Kaldi, Go} \hfill Dec 2018 -\\
Real-time biometric voice verification system developed for a leading national bank.
Integrates with the client's telephony system to process upwards of 100 MBps of
audio across hundreds of concurrent customer telephone calls and several data
centers. 200k priority customers have been enrolled into the system as of Dec
2022. The project contributes USD \$270k annually to the company.
\vspace*{2mm}

{\textbf{Prosa Console}} {\sl Python, React, Java, Keycloak, Superset} \hfill
Oct 2020 -\\
License/quota management system for internal products and APIs.
A service-based system providing a centralized SSO for employees and customers,
a public application for customers to purchase and manage plans, an admin
application for product managers and sysadmins, and BI dashboard for analysts.
Provides services for 200k registered users, handling 150k quota usage requests
per day.
\vspace*{2mm}

{\textbf{Vision Dashboard}}
{\sl Python, OpenCV, Kafka} \hfill Jun 2020 - \\
A scalable surveillance platform that allows users to add feeds/videos and apply
multiple object detectors for monitoring and analytics purposes, including face
mask detection, people distance and counting, etc.\\
\vspace*{2mm}

{\textbf{Prosa API}} 
{\sl Python, gRPC, Go, Kubernetes} \hfill April 2020 - \\
Designed and implemented parts of a scalable distributed system of speech
decoders, consisting of speech synthesis and recognition subsystems, to be used
in applications/projects within Prosa. The system is to be deployed on a
Kubernetes cluster on Google Cloud Platform (GCP).\\
\vspace*{2mm}

{\textbf{Speech Decoders}}
{\sl Python, C++, Kaldi, Merlin, gRPC} \hfill Oct 2019 - \\
Designed and implemented parts of a scalable distributed system of speech
decoders, consisting of speech synthesis and recognition subsystems, to be used
in applications/projects within Prosa. The system is to be deployed on a
Kubernetes cluster on Google Cloud Platform (GCP).\\
\vspace*{2mm}

{\textbf{Chart Builder Mandiri}} \hfill Jakarta, Indonesia \\
{\sl PHP, Javascript, SQL} \hfill Jan - Jun 2019 \\
\vspace*{1mm}
Designed and implemented the back end of a system that allows users to
dynamically define and display data sources, formulae, charts, and pages for
reports, presentations, and storage. The system has been successfully deployed
in production in the SPM group of Bank Mandiri, and is used as a module in
various other systems.\\
\vspace*{3mm}

{\textbf{WAIS BSM}} \hfill Jakarta, Indonesia \\
{\sl PHP, Javascript, SQL} \hfill Sep 2018 - \\
\vspace*{1mm}
Designed and implemented the back end of a large-scale information system for
Bank Syariah Mandiri (BSM) called the Wholesale Dashboard Information System
(WAIS). The system receives and collates data from the BSM data warehouse for
use in various analytics across the wholesale banking directorate. Further
expansions are in planning for other BSM directorates.\\
\vspace*{3mm}

{\textbf{Voice Intel}} \hfill Jakarta, Indonesia \\
{\sl Python, PHP, C++} \hfill May 2018 - Nov 2018 \\
\vspace*{1mm}
Took part in the development of a voice identification and verification system
for Badan Intelijen Nasional (BIN). The system enrolls suspects through
publically available recordings and matches them against surveillance calls to
help determine culpability.\\
\vspace*{3mm}
{\textbf{SIGI Mandiri}}  \hfill sigi2018.agranara.com\\
{\sl PHP, Javascript, SQL} \hfill Feb 2018 - \\
\vspace*{1mm}
Designed and implemented the back end to a large-scale information system for
the Government and Institutional Banking (GVI) group of Bank Mandiri HQ. A
total of 43 modules have been developed so far, with several more planned
moving forward into the third phase of development.\\
\vspace*{3mm}

\header{Publications}
\vspace{2mm}
Satriawan, C.H., Lestari, D.P. (2014). Feature-based Noise Robust Speech Recognition on an Indonesian Language Automatic Speech Recognition System.
Proc. ICEECS.\\
\vspace*{3mm}
Hoesen, D., Satriawan, C.H., Lestari, D.P., Khodra, M.L. (2016). Towards Robust Indonesian Speech Recognition with Spontaneous-speech Adapted Acoustic Models.
SLTU-2016 Workshop on Spoken Language Technologies for under-resourced
languages.\\
\vspace*{3mm}
Satriawan, C. H., Lestari, D.P. (2016). Analyzing and Classifying Indonesian Spontaneous and Dictated Speech. OCOCOSDA 2016.\\
\vspace*{3mm}
Satriawan, C. H., Lestari, D.P. (2018). Average Window Smoothing for an
Indonesian Language Online Speaker Identification System.
International Journal of Electrical Engineering and Informatics.\\

\ 
\end{document}
