\documentclass[a4paper]{article}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \textheight=10in
    \pagestyle{empty}
    \raggedright

    %\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

    \begin{document}
\vspace*{-40pt}

    

%==== Profile ====%
\vspace*{-10pt}
\begin{center}
	{\Huge \scshape {Cil Satriawan}}\\
	Bandung, Indonesia $\cdot$ cil.satriawan@gmail.com $\cdot$ (62) 821-3163-8069\\
\end{center}

%==== Education ====%
\header{Education}
\vspace{1mm}
\textbf{Institut Teknologi Bandung}\hfill Bandung, Indonesia\\
Master in Informatics Engineering \hfill Sep 2015 - Jun 2018\\
\vspace{5mm}
\textbf{Institut Teknologi Bandung}\hfill Bandung, Indonesia\\
Bachelor in Informatics Engineering \hfill Sep 2008 - October 2014\\
\vspace{5mm}

%==== Experience ====%
\header{Work Experience}
\vspace{1mm}

\textbf{Prosa} \hfill Bandung, Indonesia\\
\textit{Systems Lead} \hfill Jun 2019 -\\
\vspace{-3mm}
\begin{itemize} \itemsep 1pt
  \item Lead, manage, and supervise members of the Systems team
  \item Design and manage the development of internal systems for use
    within Prosa
\end{itemize}
\textbf{Prosa} \hfill Bandung, Indonesia\\
\textit{Speech Engineer} \hfill Jan 2018 -\\
\vspace{-3mm}
\begin{itemize} \itemsep 1pt
  \item Design and implement various speech systems
  \item Speech-related research, mostly related to speaker
    identification/verification
  \item Supervised the development of speech synthesis and recognition systems
\end{itemize}
\textbf{Agranara} \hfill Bandung, Indonesia\\
\textit{Chief Technology Officer} \hfill Dec 2017 -\\
\vspace{-3mm}
\begin{itemize} \itemsep 1pt
	\item Design and implement various large information systems in the banking
    and geospatial domains
  \item Lead and manage multiple development teams
  \item Plan and implement short and long-term strategies for continued growth and
    profitability
\end{itemize}
\textbf{Freelance Programmer} \hfill Bandung, Indonesia\\
\textit{Software Engineer} \hfill Sep 2016 - Jun 2018\\
\vspace{-3mm}
\begin{itemize} \itemsep 1pt
	\item Worked on software in various domains including speech, scientific
    visualization, and information systems
\end{itemize}
\textbf{Institut Teknologi Bandung} \hfill Bandung, Indonesia\\
\textit{Research Assistant} \hfill Sep 2015 - Sep 2017\\
\vspace{-3mm}
\begin{itemize} \itemsep 1pt
	\item Data collection, analysis, preprocessing, and training of automatic
    speech recognition and speaker identification models for meeting
    transcription with PT INTI
  \item Course/academic assistant
\end{itemize}
\textbf{Kuassa} \hfill Bandung, Indonesia\\
\textit{DSP Engineer} \hfill May 2012 - Sep 2015\\
\vspace{-3mm}
\begin{itemize} \itemsep 1pt
	\item Designed and implemented VST plugins for audio and musical applications
  \item Utilize various technologies for the digitization of analog audio
    equipment
\end{itemize}
\textbf{The British Institute} \hfill Bandung, Indonesia\\
\textit{Instructor} \hfill Oct 2008 - May 2010\\
\vspace{-3mm}
\begin{itemize} \itemsep 1pt
	\item Teach conversational and formal english courses
\end{itemize}
\vspace{3mm}

\header{Skills}
\vspace{3mm}
\begin{tabular}{ l l }
\vspace{3mm}
	Programming languages: & Python, C, C++, PHP, Go, Java, Javascript \\
	Programming domains:   & Scientific programming, Distributed systems, 
  Digital Signal Processing, \\
\vspace{3mm}
                         & Machine Learning, Web programming, Information
                         Systems, GIS \\
  Engineering management:& Aligning product development to projects \\
\vspace{3mm}
                         & Aligning research cycles to typical software
                         development cycles \\
\end{tabular}

\header{Projects}
\vspace{2mm}
{\textbf{Speech APIs}} \hfill Bandung, Indonesia \\
{\sl Python, C++} \hfill Oct 2019 - \\
\vspace{1mm}
Designed and implemented parts of a scalable distributed system of speech
decoders, consisting of speech synthesis and recognition subsystems, to be used
in applications/projects within Prosa. The system is to be deployed on a
Kubernetes cluster on Google Cloud Platform (GCP).\\
\vspace*{3mm}
{\textbf{BKN Text To Speech}} \hfill Bandung, Indonesia \\
{\sl Python, C++} \hfill Aug - Oct 2019 \\
\vspace*{1mm}
Took part in the development of a speech synthesis system used to generate
spoken questions for blind students taking part in the national exams. The
system is to be delivered by October 2019.\\
\vspace*{3mm}
{\textbf{Chart Builder Mandiri}} \hfill Jakarta, Indonesia \\
{\sl PHP, Javascript, SQL} \hfill Jan - Jun 2019 \\
\vspace*{1mm}
Designed and implemented the back end of a system that allows users to
dynamically define and display data sources, formulae, charts, and pages for
reports, presentations, and storage. The system has been successfully deployed
in production in the SPM group of Bank Mandiri, and is used as a module in
various other systems.\\
\vspace*{3mm}
{\textbf{WAIS BSM}} \hfill Jakarta, Indonesia \\
{\sl PHP, Javascript, SQL} \hfill Sep 2018 - \\
\vspace*{1mm}
Designed and implemented the back end of a large-scale information system for
Bank Syariah Mandiri (BSM) called the Wholesale Dashboard Information System
(WAIS). The system receives and collates data from the BSM data warehouse for
use in various analytics across the wholesale banking directorate. Further
expansions are in planning for other BSM directorates.\\
\vspace*{3mm}
{\textbf{Voice ID}} \hfill Jakarta, Indonesia \\
{\sl Python, C++, Java} \hfill Dec 2018 - Dec 2019 \\
\vspace*{1mm}
Designed, implemented, and lead the development of a distributed voice
identification system for the call center(s) of Bank Central Asia (BCA).
The system is desgined to allow call center agents and supervisors to enroll
and verify customers by voice, cutting down on the number of questions agents
need to ask before the customer can be verified. The system is currently in deployment and will be used to serve priority customers in two sites.\\
\vspace*{3mm}
{\textbf{Voice Intel}} \hfill Jakarta, Indonesia \\
{\sl Python, PHP, C++} \hfill May 2018 - Nov 2018 \\
\vspace*{1mm}
Took part in the development of a voice identification and verification system
for Badan Intelijen Nasional (BIN). The system enrolls suspects through
publically available recordings and matches them against surveillance calls to
help determine culpability.\\
\vspace*{3mm}
{\textbf{SIGI Mandiri}}  \hfill sigi2018.agranara.com\\
{\sl PHP, Javascript, SQL} \hfill Feb 2018 - \\
\vspace*{1mm}
Designed and implemented the back end to a large-scale information system for
the Government and Institutional Banking (GVI) group of Bank Mandiri HQ. A
total of 43 modules have been developed so far, with several more planned
moving forward into the third phase of development.\\
\vspace*{3mm}

\header{Publications}
\vspace{2mm}
Satriawan, C.H., Lestari, D.P. (2014). Feature-based Noise Robust Speech Recognition on an Indonesian Language Automatic Speech Recognition System.
Proc. ICEECS.\\
\vspace*{3mm}
Hoesen, D., Satriawan, C.H., Lestari, D.P., Khodra, M.L. (2016). Towards Robust Indonesian Speech Recognition with Spontaneous-speech Adapted Acoustic Models.
SLTU-2016 Workshop on Spoken Language Technologies for under-resourced
languages.\\
\vspace*{3mm}
Satriawan, C. H., Lestari, D.P. (2016). Analyzing and Classifying Indonesian Spontaneous and Dictated Speech. OCOCOSDA 2016.\\
\vspace*{3mm}
Satriawan, C. H., Lestari, D.P. (2018). Average Window Smoothing for an
Indonesian Language Online Speaker Identification System.
International Journal of Electrical Engineering and Informatics.\\

\ 
\end{document}
