\documentclass[11pt]{article}
    \usepackage[a4paper]{geometry}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{hyperref}
    \usepackage{textcomp}
    \usepackage{enumitem}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \textheight=10in
    \pagestyle{empty}
    \raggedright

    %\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-10pt} \hrulefill \\
}

\newcommand{\header} [1] {
    \begin{center}
      {\large \scshape {#1}}
      \lineunder
    \end{center}
    \vspace*{-8pt}
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\profile} [5] {
    \vspace*{-15pt}
    \begin{center}
        {\huge \scshape \textbf{#1}}\\
        \vspace{1mm}
        \small {#2} $\cdot$ {#3} $\cdot$ {#4} $\cdot$ {#5}
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\vspace*{-40pt}

%==== Profile ====%
\profile{Cil Satriawan}{Bandung, Indonesia}{(62)821-3163-8069}
{cil.satriawan@gmail.com}{\href{https://www.linkedin.com/in/cil-satriawan-a60601111}{LinkedIn}}

%==== Cover Letter ====%
\header{Cover Letter}
\vspace{1mm}

Five years ago, I would have scoffed at the idea of AGI being achieved within
our lifetimes. Recent advances have had me reconsidering, and seeing the
singularity fast approaching, I would like to stay on the right side of the
event horizon; that is, with Synthesia. At this rate, I believe AI-aided media
generation for businesses, catered to their individual users, will be the norm
within the decade. It would be my pleasure to discuss the ways I could
contribute to the continued success of this approach and the Synthesia team.
\vspace{3mm}

I am an engineer and manager currently based in Bandung, Indonesia. I am
relocating to London in 2023, where my partner will be pursuing a postgraduate
degree. In the past 5 years I have founded a software house and joined a
start-up, both of which I am currently active in. As founder of a software
house, I am involved in both business and technical decisions, often assuming
PM duties and interacting with clients as needed. As VP Engineering of an AI
start-up, I am responsible for hiring, onboarding, KPIs, and growing teams. In
both cases, I maintain high-level technical duties surrounding design and
architecture, and regularly conduct code reviews and implement features.
\vspace{3mm}

As an engineer and manager, I believe my main strength lies in technical
ownership. Whether as a team member or leader, I want to see our software
delivered and used. When I believe things are moving too slowly or aimlessly, I
will prod PMs for specifications and engineers for designs. I believe there is
real value in moving fast, but am rarely willing to compromise technically or
accumulate too much technical debt. In the organizations I currently work for, I
often handle the internal "products" used as infrastructure by various teams,
mostly acting as owner and occasionally engineer.
\vspace{3mm}

I find satisfaction when various disparate elements click together to achieve a
single purpose, be it for software systems or teams of people. I am usually
there to facilitate the building process, ensuring it can be done reliably,
sustainably, and efficiently. In teams as in systems, I have learnt that
communication is key: Transparency, clarity, brevity, and a large degree of
tolerance is needed to make teams and teams of teams function robustly. I
believe I can bring this experience with me as an engineer at Synthesia, and
further advance this skill for the benefit of the organization.
\vspace{3mm}

I would be delighted to discuss the ways in which I could contribute to the
Synthesia team in greater detail. I look forward to hearing from you.
\vspace{3mm}

Kind regards,\newline
Cil Satriawan

\ 
\end{document}
